Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-03-09 manuscript/climate_sensitivity_draft.Rmd
redid word count
#82

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  currently ~5855 (strict limit 6,500)	 |	No. of figures | 	2 (both colour)
Summary|  	currently 194 (limit 200) | 	No. of Tables | 	5  
Introduction|	currently ~1468 |	No of Supporting Information files | 	6
Materials and Methods |	currently ~2162	||	 
Results |	currently ~674	 ||
Discussion |	currently ~1551 (limit 30% of total (not strict), or 1950 if manuscript reaches word limit)	||
Acknowledgements | currently ~124	||

>>>>

Text | word count | other | n
---------------------------------------------|---------------------|-----------------------------|--------------------
Total word count (excluding summary, references and legends) |  5,365	 |	No. of figures | 	2 (both colour)
Summary|  	198 | 	No. of Tables | 	5  
Introduction|	1,034 |	No of Supporting Information files | 	6
Materials and Methods |	1,945	||	 
Results |	697	 ||
Discussion |	1467	||
Acknowledgements | 125	||
